Computing volume via non-linear rectangular infinitesimals

### 2019-08-14 Cav2D/article-template.tex
progress with prismatoid section

\section{Prismatoid}
Let $\mathcal{S}$ be the solid which is bounded by the planes $f(x,y)=-x-y+8$, $2x$, $2(x-4)$, $y$, $y-4$ and the $xy$-plane. Solid $\mathcal{S}$ is depicted 
in Figure~\ref{fig:prismatoid_solid}, Figure~\ref{fig:prismatoid} and Figure~\ref{fig:prismatoid_real}. Solid $\mathcal{S}$ is a prismatoid, since all of its 
vertices lie in two parallel planes. Furthermore, all of its lateral faces are trapezoids or triangles. Note that, the line of intersection between $2x$ and $y$ is $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$.
The line $\mathbf{c}(t)$ is depicted and labelled in Figure~\ref{fig:prismatoid_solid}.

As we alluded to in the previous section we can calculate $V_{\mathcal{S}}$ using the double Cavalieri integral:
\begin{equation}
\iint\limits_{\!\mathcal{C}} f(x,y) dA =  \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy,
\end{equation}
with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We can, however, only evaluate the above integral if the transformation $T$ is known (see Figure ). We can find $T$ using Equation

>>>>

\section{Prismatoid}
Let $\mathcal{S}$ be the solid which is bounded by the planes $f(x,y)=-x-y+8$, $2x$, $2(x-4)$, $y$, $y-4$ and the $xy$-plane. Solid $\mathcal{S}$ is depicted 
in Figure~\ref{fig:prismatoid_solid}, Figure~\ref{fig:prismatoid} and Figure~\ref{fig:prismatoid_real}. Solid $\mathcal{S}$ is a prismatoid, since all of its 
vertices lie in two parallel planes. Furthermore, all of its lateral faces are trapezoids or triangles (if viewed from the side). Also note the following: the base of $\mathcal{S}$ is the region 
 $R = [0,4]\times [0,4]$ and that the line of intersection between $2x$ and $y$ is $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$. The region $R$ and the line $\mathbf{c}(t)$ are
also depicted and labelled in Figure~\ref{fig:prismatoid_solid}.\\

\noindent
As we alluded to in the previous section we can calculate $V_{\mathcal{S}}$ using the double Cavalieri integral:
\begin{equation}
\iint\limits_{\!\mathcal{C}} f(x,y) dA =  \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy,
\end{equation}
with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We can, however, only evaluate the above integral if the transformation $T$ is known (see Figure ). We can find $T$ using Equation
